Proof of Identity

### 2022-06-26 paper.tex
enough for today

\newpage
\section{On chain code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo Solidity
//Key is eID private key, or PrivateeIDKey("")
//PersonKey is Blockchain key used by a Person
contract IdentitiesManager {
  //all the mappings are mappings where uint256 is a hash!
  mapping(uint256 => uint256) public NinKidUsed;
  mapping(uint256 => uint256) public NinKidKpUsed;
  mapping(uint256 => uint256) public NinKidKpLastConfirmed;
  mapping(uint256 => bool) public KpInvalid;
  mapping(uint256 => bool) public KidInvalid;
  //TODO:CA fields!

  //vKid=KidPrivate("registerKid")
  //Nin=H(Nin)
  function registerKid public(
    uint256 Nin,
    uint256 vKid,
    bytes proofNinOwnsKid
  ){
    uint256 previousKey = NinKidUsed[Nin];
    if(previousKey == vKid)
      return;
    bool isOwner = zksnarkverify(VK, [
        Nin, 
        vKid
      ],
      proofPINOwnsKid);
    if(isOwner && ! KidInvalid[vKid]){
      if(previousKey!=0)
        KidInvalid[previousKey]=true;
      NinKidUsed[Nin]=vKid;
    }
  }

  //PinK=H(Pin, K_1("registerP")) which is != H(Pin, K_1("registerK"))
  //PinK can not be connected to Pin, unless one knows K_1
  function registerP public(
    uint256 PinK,
    uint256 PinKP,
    bytes proof
  ){
    uint256 previousKey = PinKPUsed[PinK]
    if(previousKey == PinK)
      return; //already registered

    //zkp(
      //K!invalid
        //?Need KInvalid to be Zero Knowledge Set (ZKS), and to get roots
      //CA!invalid
      //CA -> K -> Pin
      //PinK=H(Pin, K_1("registerP"))
      //PinKP=H(Pin, K_1("registerP"), P_1("registerP"))
    //)
    bool ok = zksnarkverify(VK, [
    ], proof);

    if(ok && ! PInvalid[PinKP]){
      if(previousKey != 0)
        PInvalid[previousKey]=true;
      PinKPUsed[PinK]=PinKP;
      PinKPLastConfirmed[PinK]=block.number;
    }

>>>>

\newpage
\section{On chain code}
\begin{lstlisting}[language=C, frame=single, style=b]
//pseudo Solidity
contract IdentitiesManager {
  //all the mappings are mappings where uint256 is a hash!
  mapping(uint256 => uint256) public NinKidUsed;
  mapping(uint256 => uint256) public NinKidKpUsed;
  mapping(uint256 => uint256) public NinKidKpLastConfirmed;
  mapping(uint256 => bool) public KpInvalid;
  mapping(uint256 => bool) public KidInvalid;
  //TODO:CA fields!

  //hNin=H(Nin)
  //vKid=KidPrivate("registerKid")
  function registerKid public(
    uint256 hNin,
    uint256 vKid,
    bytes proofNinOwnsKid
  ){
    uint256 previousKey = NinKidUsed[hNin];
    if(previousKey == vKid)
      return;
    bool isOwner = zksnarkverify(VK, [
        hNin, 
        vKid
      ],
      proofPINOwnsKid);
    if(isOwner && ! KidInvalid[vKid]){
      if(previousKey!=0)
        KidInvalid[previousKey]=true;
      NinKidUsed[hNin]=vKid;
    }
  }

  //look into the paper.pdf for meaning of args
  function registerKp public(
    uint256 NinKid,
    uint256 NinKidKp,
    bytes proof
  ){
    uint256 previousKey = NinKidKpUsed[NinKid]
    if(previousKey == NinKid)
      return; //already registered

    //zkp(
      //K!invalid
        //?Need KInvalid to be Zero Knowledge Set (ZKS), and to get roots
      //CA!invalid
      //CA -> K -> Nin
      //NinKid=H(Nin, KidPrivate("registerP"))
      //NinKidKp=H(Nin, KidPrivate("registerP"), KpPrivate("registerP"))
    //)
    bool ok = zksnarkverify(VK, [
      NinKid,
      NinKidKp
    ], proof);

    if(ok && ! PInvalid[NinKidKp]){
      if(previousKey != 0)
        PInvalid[previousKey]=true;
      NinKidKpUsed[NinKid]=NinKidKp;
      NinKidKpLastConfirmed[NinKid]=block.number;
    }
